Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-09-14 manuscript/climate_sensitivity_draft.Rmd
working on results
#131

We then determined the top full models for predicting each dependent variable. 
To do so, we compared models with all possible combinations of candidate variables, including $ln[H]$*$ln[TWI]$ and species traits as specified above.
We identified the full set of models within $\Delta$AICc=2 of the best model (that with lowest AICc). 
When a variable appeared in all of these models and the sign of the coefficient was consistent across models, we viewed this as support for the acceptance/rejection of the associated prediction (Table 1). 
If the variable appeared in some but not all of these models, and its sign was consistent across models, we considered this partial support/rejection. 
Visualization of the best mixed effects model per drought scenario was created by the visreg package [@R-visreg].

@@

Taller trees (based on $H$ in the drought year) showed stronger growth reductions during drought (Table 1; Fig. **4**). 
Specifically, $ln[H]$ appeared, with a negative coefficient, in the best model ($\Delta$AICc=0) and all top models when evaluating the three drought years together (Tables S8-S9). 
The same held true for 1966 individually.
For the 1977 drought, $ln[H]$ did not appear in the best model, but was included, with a negative coefficient, among the top models--*i.e.*, models that were statistically indistinguishable ($\Delta$AICc<2) from the best model (Tables 1, S6-S9). 
For the 1999 drought, $ln[H]$ had no significant effect.

$Rt$ had a significantly negative response to $ln[TWI]$ across all drought years combined (Fig. **4**, Table S8-S9). 
The effect was also significant for 1977 and 1999 individually (Fig. **4**, Table S8).
When $Rt_{ARIMA}$ was used as the response variable, the effect was significant in 1977, and included in some of the top models in 1966 and 1999 (Table S9).
This negates the idea that trees in moist microsites would be less affected by drought. 
Nevertheless, we tested for a $ln[H] *ln[TWI]$ interaction, a negative sign of which could indicate that smaller trees (presumably with smaller rooting volume) are more susceptible to drought in drier microenvironments with a deeper water table. 
This hypothesis was rejected, as the $ln[H] *ln[TWI]$ interaction was never significant, and had a positive sign in any top models in which it appeared (Tables 1, S8-S9).
This term did appear with a positive coefficient in the best $Rt_{ARIMA}$ model for all years combined (Table S9), indicating that the negative effect of height on  $Rt$ was significantly stronger in wetter microhabitats.

>>>>

We then determined the top full models for predicting each dependent variable. 
To do so, we compared models with all possible combinations of candidate variables, including $ln[H]$*$ln[TWI]$ and species traits as specified above.
We identified the full set of models within $\Delta$AICc=2 of the best model (that with lowest AICc). 
When a variable appeared in all of these models and the sign of the coefficient was consistent across models, we viewed this as support for the acceptance/rejection of the associated prediction (Table 1). 
If the variable appeared in some but not all of these models, and its sign was consistent across models, we considered this partial support/rejection.

@@

Taller trees (based on $H$ in the drought year) showed stronger growth reductions during drought (i.e., lower $Rt$) and less resilience following drought (i.e., lower $Rc$ and $Rs$; Table 1; Fig. **4**). 
Specifically, for $Rt$, $ln[H]$ appeared, with negative coefficient, in the best model ($\Delta$AICc=0) and all top models when evaluating the three drought years together (Tables S8-S9). The same held true for 1966 individually, but there was no significant effect of $ln[H]$ for 1977 or 1999 individually. 
For $Rc$, $ln[H]$ appeared, with negative coefficient, in the best model without a $ln[H] *ln[TWI]$ interaction, for the three drought years together and for 1977, but not for 1966 or 1999.
For $Rs$, again considering the best models without a $ln[H] *ln[TWI]$ interaction, there was a negative effect of $ln[H]$ for the three drought years together and for 1966 and 1977, and a non-significant negative trend in 1999.

**RESUME HERE**
$Rt$ had a significantly negative response to $ln[TWI]$ across all drought years combined (Fig. **4**, Table S8-S9). 
The effect was also significant for 1977 and 1999 individually (Fig. **4**, Table S8).
When $Rt_{ARIMA}$ was used as the response variable, the effect was significant in 1977, and included in some of the top models in 1966 and 1999 (Table S9).
This negates the idea that trees in moist microsites would be less affected by drought. 
Nevertheless, we tested for a $ln[H] *ln[TWI]$ interaction, a negative sign of which could indicate that smaller trees (presumably with smaller rooting volume) are more susceptible to drought in drier microenvironments with a deeper water table. 
This hypothesis was rejected, as the $ln[H] *ln[TWI]$ interaction was never significant, and had a positive sign in any top models in which it appeared (Tables 1, S8-S9).
This term did appear with a positive coefficient in the best $Rt_{ARIMA}$ model for all years combined (Table S9), indicating that the negative effect of height on  $Rt$ was significantly stronger in wetter microhabitats.

### 2020-09-14 manuscript/tables&figures.Rmd
remove column for Rt_arima
@mcgregorian1 , I think it's overkill to list Rt_arima sample sizes in a separate column, so reverted back to former system for Rt.
#139
working on results
#131

Sample sizes are after removal of outliers. Dashes indicate that the variable was available for all records. 
*Sample sizes of independent variables refer to the $Rt$ model.

@@

![**Figure 4. Visualization of best statistical models for drought resistance ($Rt$), recovery ($Rc$), and resilience ($Rs)$ for all droughts combined and for each individual drought year.** Confidence intervals were defined via bootsrapping in the bootpredictlme4 package. Model coefficients are given in Tables S8 and S10-11. ](tables_figures/publication/Figure4_model_vis_all.png)

>>>>

Sample sizes are after removal of outliers. Dashes for sample sizes of independent variables indicate that the variable was available for all records. Xylem porosity sample sizes are sums across all drought years.

*Sample sizes of independent variables refer to the $Rt$ model.

@@

![**Figure 4. Visualization of top statistical models for drought resistance ($Rt$), recovery ($Rc$), and resilience ($Rs)$ for all droughts combined and for each individual drought year.** For cases where the best model includes a DBH x TWI interaction ($Rc$ in all droughts and 1966, $Rs$ in all droughts and 1977), we plot the best model without the interaction. Visualization of the best mixed effects model per drought scenario was created by the visreg package [@R-visreg], and confidence intervals were defined via bootsrapping in the bootpredictlme4 package. Model coefficients are given in Tables S8 and S10-11. ](tables_figures/publication/Figure4_model_vis_all.png)
